Model LF

### 2022-09-30 max_dp endogen stød.Rmd
commit

COMMENT> Lavet for at kunne støde til g 
IDENTITY> wage_growth
EQ> wage_growth = TSDELTA(wage_ds,4)/TSLAG(wage_ds,4)

COMMENT> Lavet for at kunne støde til g 
IDENTITY> net_export
EQ> net_export = xk_ds - mk_ds

@@

COMMENT> Rate of capacity utilization
IDENTITY> u
EQ> u=yk/(bd_nfc_k+equip_nfc_k)

@@

S_modelData$wage_growth = wage_growth

@@

max_dp_growth=stat_tilpas_00 + stat_reg_00

net_export_00=xk_ds_00 - mk_ds_00

plot(max_dp_growth);lines(wage_growth_00, col= "blue")
```

@@

@@

>>>>

@@

COMMENT> Rate of capacity utilization
IDENTITY> u_ds
EQ> u_ds=yk_ds/(bd_nfc_k+equip_nfc_k)

@@

#S_modelData$wage_growth = wage_growth

@@

@@

shock_kuld_07 = Shock_7$simulation$shock_kuld

@@

plot(shock_kuld_07, col= "red"); lines(shock_kuld_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
